The Language Demographics of Amazon Mechanical Turk : Response to Reviewers

### 2013-11-15 writeup/reviewer-response/paper.tex
rewrite

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfloat}
\usepackage{subcaption}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{5cm}    % Expanding the titlebox

@@

\begin{figure}
\centering
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{figures/fig2with.png}
\caption{All turkers.}                
\label{dist}
\end{subfigure}
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{figures/fig2without.png}
\caption{Turkers with \textless 60\% overlap with Google Translate.}
\label{cdf}
\end{subfigure}
\caption{Qualities for languages with \textgreater 50 turkers. Dark blue shows quality measured by perfect match on the control translation. Light blue indicates quality measured by included synonymous translations.}\label{qual}
\end{figure}

@@

@@

Previous work by Matt Post in the 2010 WMT has demonstrated not only that turkers are able to provide high quality translations of complete sentences, but also that these translations, when added into an SMT pipeline, measurably improve translation quality. \textbf{MORE HERE.}

@@

\section{Novelty}

Its novel. Trust us.

>>>>

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfloat}
\usepackage{subcaption}

\setlength\titlebox{5cm}    % Expanding the titlebox

@@

\begin{figure}
\centering
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{figures/fig2all_errorbars.png}
\caption{All turkers.}                
\label{dist}
\end{subfigure}
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{figures/fig2filter_errorbars.png}
\caption{Turkers with \textless 60\% overlap with Google Translate.}
\label{cdf}
\end{subfigure}
\caption{Qualities for languages with \textgreater 50 turkers. Dark blue shows quality measured by perfect match on the control translation. Light blue indicates quality measured by included synonymous translations.}\label{qual}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{figures/turker_hit_contributions.png}
\caption{Contributions of individual turkers to the overall number of HITs in each language. The dark blue bar represents the proportion of total HITs which were completed by the 10 highest-contributing turkers. The next darkest bar represents the next 10 highest-contributing turkers, and likewise for the thrid and forth darkest. The final bar represents the remaining turkers which were not one of the top 40 contributors.}
\label{numhits}
\end{figure}

@@

Previous work by Matt Post in the 2010 WMT has demonstrated not only that turkers are able to provide high quality translations of complete sentences, but also that these translations, when added into an SMT pipeline, measurably improve translation quality.

\begin{table}[t]
\centering
\begin{tabular}{l|rr}
  language  & SAMT &  Google \\
  \hline\hline
  Bengali    & 13.53  &  20.01 \\
  Hindi      & 17.29  & 25.21 \\  
  Malayalam    & 14.28  & - \\      
  Tamil      &  9.85  &  13.51 \\  
  Telugu     & 12.61  & 16.03  \\  
  Urdu        & 20.99  & 23.09 \\   
\end{tabular}
\caption{BLEU scores translating into English (four references).  BLEU
scores are the mean of three MERT runs.}
\label{table:bleu}
\end{table}

\begin{figure*}[t]
  \centering
  \includegraphics[width=\textwidth]{figures/tamil.png}
  \begin{tabular}{l}
    \hline
    In March 15,2007 Wiki got a place in Oxford English dictionary. \\
    On March 15, 2007 wiki was included in the Oxford English
    dictionary. (5) \\
    ON MARCH 15, 2007, WIKI FOUND A PLACE IN THE OXFORD ENGLISH
    DICTIONARY \\
    March 15, 2007 oxford english index of wiki's place. \\ \\

  \end{tabular}
  \caption{An example of the variance in translation quality for the
    human translations of a Tamil sentence; the formatting of the
    translations has been preserved exactly.  The parenthesized number
    indicates the number of votes received in the voting task
    (\S\ref{section:votes}).}
  \label{figure:variance}
\end{figure*}

@@
